Library Parser

### 2024-06-15 preregistration/preregistration.qmd
update prereg, extraction details

metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    title = "Music emotion recognition: Meta-analysis of regression and classification success of emotion ratings from audio",
    authors = "Eerola, T., Anderson, C.",
    start_date = "2024-05-15",
    tasks_and_roles = "equal contribution",
    target_discipline = "music cognition, music information retrieval, music psychology"
  ) |>
  preregr::prereg_show_item_completion(
    section="metadata"
  );
# validate
metamer_prereg |>
  preregr::prereg_show_item_content(
    section="metadata"
  );

@@

metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    type_of_review = "Meta-analysis",
    review_stages = "Search, Screening, Extraction, Synthesis",
    current_stage = "Screening",
    start_date = "2024-05-15",
    end_date = "2024-06-30",
    background ="The aim is to establish the current state of the model success in predicting emotions expressed by music from audio. We will focus on the last 10 years of research and especially the research that has predicted valence and arousal ratings from music audio. No such analysis exists and there are interesting challenges in predicting emotional content of music that relates to specificity of the music and the type of emotions and features used that would benefit from a systematic analysis.",
    primary_research_question = "To what degree can arousal and valence ratings of emotions expressed by music be predicted from audio? How are the prediction rates related to genres of music, the type of models used, the type of features, modelling design and cross-validation utilised, and the model complexity and parsimony?",
    secondary_research_question = "What is the prediction rate related to classification of quadrants in the affective circumplex?",
    expectations_hypotheses = "Prediction of arousal ratings is generally high and robust, and in terms of the model outcome metrics (correlation), achieves at least r = 0.77 (R square of 0.60). Prediction of valence ratings from audio is more challenging and more context dependent and will achieve generally a lower prediction rate, r = 0.63 (R square 0.40)",
    dvs_outcomes_main_vars = "Regression model performance will be converted to pearson correlation coefficients and classification model performance will be converted to Matthews correlation coefficient (MCC) when possible.",
    ivs_intervention_treatment = "Music genre, prediction type (linear or classification), feature type (based on prior work by Panda et al., 2020), model complexity (high, medium, low), model validation (exist or not)",
    software = "R and Github repository",
    funding = "Mitacs Globalink Research Award (Mitacs & British High Commission - Ottawa, Canada)",
    cois = "There are no identified conflicts of interests.",
    overlapping_authorships = "Not applicable"
  )

@@

metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    screening_stages = "We completed screening using custom fields inserted to the bibtex file and managed with citation managers (jabref and bibdesk). To filter relevant studies, we followed a three-stage screening procedure. <BR> <B>In stage 1</B>, we screened the 553 studies’ titles for relevance, removing irrelevant studies and recording exclusion criteria (see Used exclusion criteria). CA assigned 63 studies to the High Priority based on titles’ relevance, assigned 338 studies to Low Priority based on irrelevant titles, 152 studies to Medium Priority for additional screening. <BR><B>In stage 2</B>, CA assessed the 152 Medium Priority studies for relevance by screening abstracts. 105 studies’ status changed to Low Priority, whereas 30 studies’ status changed to High Priority. 27 studies remained in the Medium priority category. TE and CA evaluated the remaining 27 studies’, moving 15 to the High Priority Category and 12 to the Medium Priority Category. For studies moved to Low Priority, brief BiBTex comments summarized the rationale for exclusion. <BR><B>In stage 3</B>, TE and CA independently screened Priority 1 studies for relevance, including an <I>include</I>, <I>exclude</I>, or <I>unsure</I> decision in a user-comment BiBTeX field.",
    screened_fields_masking = "We left authors, titles, publication years, and journal names unmasked.",
    used_exclusion_criteria = "We excluded studies according to the following exclusion criteria: soundscapes/vocalisations, non-music audio, video clips, physiological markers, dance, video/movie, physiological/EEG/ECG/MEG/GSR/brain imaging/heart rate/neuroscience/brain studies, sensor data, multimodal, autism, ageing, review/systematic review/overview/survey, face emotion recognition, mental health, music therapy, schizophrenia, memory/emotion factors as IVs, recommender systems, or systems that identify the location of emotional excerpts.",
    screener_instructions = "As described above.",
    screening_reliability = "In the pass 1 and 2, we will have a quality control check after the pass to discuss the identified categories. In the third pass, we double-coded decisions, resolving discrepancies through discussion.",
    screening_reconciliation_procedure = "We reconcile discrepancies through discussion, resolving “unsure” votes first, followed by discrepancies in include/exclude decisions between authors Results of this updating procedure are available in the <A HREF=https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html>Pass 3 comparison document</A>.",
    sampling_and_sample_size = "We identified and retained 553 articles from Scopus, Web of Science, and Open Alex based on the search strategy outlined above. See table at the end that details the cumulative exclusions.",
screening_procedure_justification = "To offer a broad summary of music emotion recognition tasks, we attempted to include all studies involving prediction with acoustic features. We performed screening unblinded and determined inclusion/exclusion criteria based on studies’ relevance to the task explored.",
screening_data_management_and_sharing = "Sources will be shared as (a) BibTeX library(ies) including reviewer notes."
)

#### Section: Extraction ------
metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    entities_to_extract = "These are listed and defined in 
    <A HREF=https://tuomaseerola.github.io/metaMER/studies/extraction_details.html>extraction details</A>.",
    extraction_stages = "The data extraction done is stages. In the first stage, an extraction pass of the collection is done by ca using our initial entities to extract document. The challenges are discussed and the entities are revised.",
    extractor_instructions = "See <A HREF=https://tuomaseerola.github.io/metaMER/studies/extraction_details.html>extraction details</A>.",
    extractor_blinding = "Blinding was not used.",
    extraction_reliability = "CA will perform extractions; TE will verify extractions for quality assurance.",
    extraction_reconciliation_procedure = "Discussion and joint decision for studies where extraction proves to be challenging and issues of interpretation arise.",
    extraction_procedure_justification = "These are documented in the extraction details.",
    extraction_data_management_and_sharing = "We retain the information of the studies in shared bibtex files, extraction data will be stored in ascii data files (.bibtex), and the parser for reading the data from .bibtex files to R for the analysis will be available (as quarto/markdown/R files), and all these are managed, structured, shared and documented in Github repository according to FAIR principles.",
    misc_extraction_details = "NA"
  )

@@

>>>>

metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    title = "Music emotion recognition: Meta-analysis of regression and classification success of emotion ratings from audio",
    authors = "Eerola, T., Anderson, C. J.",
    start_date = "2024-05-15",
    tasks_and_roles = "equal contribution",
    target_discipline = "music cognition, music information retrieval, music psychology"
  ) |>
  preregr::prereg_show_item_completion(
    section="metadata"
  );
# validate
metamer_prereg |>
  preregr::prereg_show_item_content(
    section="metadata"
  );

@@

metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    type_of_review = "Meta-analysis",
    review_stages = "Search, Screening, Extraction, Synthesis",
    current_stage = "Screening",
    start_date = "2024-05-15",
    end_date = "2024-06-30",
    background ="The aim is to establish the current state of the model success in predicting emotions expressed by music from audio. We will focus on the last 10 years of research and especially the research that has predicted valence and arousal ratings from music audio. No such analysis exists and there are interesting challenges in predicting emotional content of music that relates to specificity of the music and the type of emotions and features used that would benefit from a systematic analysis.",
    primary_research_question = "To what degree can arousal and valence ratings of emotions expressed by music be predicted from audio? How are the prediction rates related to genres of music, the type of models used, the type of features, modelling design and cross-validation utilised, and the model complexity and parsimony?",
    secondary_research_question = "What is the prediction rate related to classification of quadrants in the affective circumplex?",
    expectations_hypotheses = "Prediction of arousal ratings is generally high and robust, and in terms of the model outcome metrics (correlation), achieves at least r = 0.77 (R square of 0.60). Prediction of valence ratings from audio is more challenging and more context dependent and will achieve generally a lower prediction rate, r = 0.63 (R square 0.40)",
    dvs_outcomes_main_vars = "Regression model performance will be converted to Pearson correlation coefficients and classification model performance will be converted to Matthews correlation coefficient (MCC) when possible.",
    ivs_intervention_treatment = "Music genre, prediction type (linear or classification), feature type (based on prior work by Panda et al., 2020), model complexity (high, medium, low), model validation (exists or not)",
    software = "R and Github repository",
    funding = "Mitacs Globalink Research Award (Mitacs & British High Commission - Ottawa, Canada)",
    cois = "There are no identified conflicts of interests.",
    overlapping_authorships = "Not applicable"
  )

@@

metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    screening_stages = "We completed screening using custom fields inserted to the bibtex file and managed with citation managers (jabref and bibdesk). To filter relevant studies, we followed a three-stage screening procedure. <BR> <B>In stage 1</B>, we screened the 553 studies’ titles for relevance, removing irrelevant studies and recording exclusion criteria (see Used exclusion criteria). CA assigned 63 studies to the High Priority based on titles’ relevance, assigned 338 studies to Low Priority based on irrelevant titles, and 152 studies to Medium Priority for additional screening. <BR><B>In stage 2</B>, CA assessed the 152 Medium Priority studies for relevance by screening abstracts. 95 studies’ status changed to Low Priority, whereas 30 studies’ status changed to High Priority. 27 studies remained in the Medium priority category. TE and CA evaluated the remaining 27 studies’, moving 15 to the High Priority Category and 12 to the Medium Priority Category. For studies moved to Low Priority, brief BiBTex comments summarized the rationale for exclusion. <BR><B>In stage 3</B>, TE and CA independently screened Priority 1 studies for relevance, including an <I>include</I>, <I>exclude</I>, or <I>unsure</I> decision in a user-comment BiBTeX field.",
    screened_fields_masking = "We left authors, titles, publication years, and journal names unmasked.",
    used_exclusion_criteria = "We excluded studies according to the following exclusion criteria: soundscapes/vocalisations, non-music audio, video clips, physiological markers, dance, video/movie, physiological/EEG/ECG/MEG/GSR/brain imaging/heart rate/neuroscience/brain studies, sensor data, multimodal, autism, ageing, review/systematic review/overview/survey, face emotion recognition, mental health, music therapy, schizophrenia, memory/emotion factors as IVs, recommender systems, or systems that identify the location of emotional excerpts. We included results from some studies meeting exclusion criteria (e.g., multimodal studies involving physiological measurements) if they reported separately on acoustic-only models.",
    screener_instructions = "As described above.",
    screening_reliability = "In the pass 1 and 2, we included a quality control check after the pass to discuss the identified categories. In the third pass, we double-coded decisions, resolving discrepancies through discussion.",
    screening_reconciliation_procedure = "We reconcile discrepancies through discussion, resolving “unsure” votes first, followed by discrepancies in include/exclude decisions between authors Results of this updating procedure are available in the <A HREF=https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html>Pass 3 comparison document</A>.",
    sampling_and_sample_size = "We identified and retained 553 articles from Scopus, Web of Science, and Open Alex based on the search strategy outlined above. See table at the end that details the cumulative exclusions.",
screening_procedure_justification = "To offer a broad summary of music emotion recognition tasks, we attempted to include all studies involving prediction with acoustic features. We performed screening unblinded and determined inclusion/exclusion criteria based on studies’ relevance to the task explored.",
screening_data_management_and_sharing = "Sources will be shared as (a) BibTeX library(ies) including reviewer notes."
)

#### Section: Extraction ------
metamer_prereg <-
  metamer_prereg |>
  preregr::prereg_specify(
    entities_to_extract = "These are listed and defined in 
    <A HREF=https://tuomaseerola.github.io/metaMER/studies/extraction_details.html>extraction details</A>.",
    extraction_stages = "The data extraction will be completed in stages. In the first stage, CA will complete a pass of the collection using our initial entities to extract document. The challenges are discussed and the entities are revised.",
    extractor_instructions = "See <A HREF=https://tuomaseerola.github.io/metaMER/studies/extraction_details.html>extraction details</A>.",
    extractor_blinding = "Blinding was not used.",
    extraction_reliability = "CA will perform extractions; TE will verify extractions for quality assurance.",
    extraction_reconciliation_procedure = "Discussion and joint decision for studies where extraction proves to be challenging and issues of interpretation arise.",
    extraction_procedure_justification = "These are documented in the extraction details.",
    extraction_data_management_and_sharing = "We retain the information of the studies in shared bibtex files, extraction data will be stored in ascii data files (.bibtex), and the parser for reading the data from .bibtex files to R for the analysis will be available (as quarto/markdown/R files), and all these are managed, structured, shared and documented in Github repository according to FAIR principles.",
    misc_extraction_details = "NA"
  )

@@

- Panda, R., Malheiro, R., & Paiva, R. P. (2020). Audio features for music emotion recognition: a survey. IEEE Transactions on Affective Computing, 14(1), 68-88.
[https://doi.org/10.1109/TAFFC.2020.3032373](https://doi.org/10.1109/TAFFC.2020.3032373)

### 2024-06-15 studies/extraction_details.qmd
update prereg, extraction details

## PARADIGM

Paradigm used for MER task. Either `classification` or `regression`.

@@

## EMOTIONS

List of emotion names or labels separated by commas. **TODO:** Discuss potential redundancies with `MODEL_RATE_EMOTION_NAMES`

@@

Number of stimuli employed in experiment.\
**TODO** Discuss handling of subset selection, train, test, etc

@@

Number of features included in model. **TODO** Discuss handling of subset selection, train, test, etc

@@

Total number of participants in experiment. **TODO** Discuss handling of secondary information. E.g., MediaEval

@@

Nature of rating/classification task undertaken by participants. E.g., rate, annotate. **TODO** discuss multi-stage studies. E.g., MediaEval categories validated by participants using AV ratings.

@@

**TODO** Discuss feasibility of this approach. Other nominalizations/categories not covered (e.g., spectral, temporal, lyric)

@@

Name(s) of feature analysis toolboxes. **TODO** Discuss original features (as in `Panda2020no`)

@@

Name of model type. One of regression, classification *TODO* Discuss redundancy with `PARADIGM`. Consider cases where regression and classification employed; or regression approach to classification (e.g., `sorussa2020em`)

@@

Additional information pertaining to predictive model, such as the name of algorithm used and other pertinent parameters. E.g., RandomForest, Commonality Analysis, Multiple Regression, Neural Networks, LDSM, etc. *TODO* Discuss how much information to include.

@@

Metric used in model evaluation. E.g., 'R2' for $R^2$, MSE, CCC, Classification accuracy, etc.

@@

Additional information pertaining to predictive model. Format as R code when encoding multiple pertinent parameters. E.g., `c(training_epochs = 100, layer_n = c(1,2), lstm_units = c(124, 248))`

@@

Pertinent prediction of model summaries. Report as *R* arrays, including summary statistics in variables. When reporting results of multiple models, concatenate multiple entries with `rbind`. When reporting results for different toolboxes or feature subsets, assign each to a new BiBTeX field with relevant identifier following final underscore.

\### EXAMPLES:

#### Regression

Report relevant summary statistics in R code. Different feature distinguished through BiBTeX fields (`MODEL_RATE_EMOTION_VALUES_MFCC`, `MODEL_RATE_EMOTION_VALUES_ESSENTIA` ). Fitted models concatenated with `rbind` (`linear.regression`, `SMOreg`, `RNN1.124LSTM`, etc.). Model results reported with names in first array (`R2_arousal`, `MAE_arosal`, `R2_valence`, `MAE_valence`), and recycled in each subsequent model.

```         
MODEL_RATE_EMOTION_VALUES_MFCC = {
  rbind(
    linear.regression = c(R2_arousal = 0.61, MAE_arousal = 0.13, R2_valence = 0.07, MAE_valence = 0.17),
    SMOreg = c(0.6,0.13,0.10,0.17),
    RNN1.124LSTM = c(0.58,0.14,0.14,0.17),
    RNN2.124.124LSTM = c(0.66,0.12,0.11,0.16),
    RNN3.248LSTM = c(0.61,0.13,0.13,0.16),
    RNN4.248.248LSTM = c(0.64,0.12,0.14,0.15)
  )
},
MODEL_RATE_EMOTION_VALUES_ESSENTIA = {
  rbind(
    linear.regression = c(R2_arousal = 0.07, MAE_arousal = 0.25, R2_valence = 0.06, MAE_valence = 0.19),
    SMOreg = c(0.48,0.18,0.27,0.17),
    RNN1.124LSTM = c(0.54,0.14,0.21,0.16),
    RNN2.124.124LSTM = c(0.67,0.12,0.32,0.13),
    RNN3.248LSTM = c(0.58,0.14,0.32,0.14),
    RNN4.248.248LSTM = c(0.69,0.11,0.40,0.13),
    RNN5.529LSTM = c(0.61,0.13,0.29,0.15),
    RNN6.529.529LSTM = c(0.68,0.12,0.36,0.14)
  )
}
```

#### Classification

Report confusion matrices as *R* arrays. The following example classifies emotions into five categories for multiple feature subsets. Different feature distinguished through BiBTeX fields (`MODEL_RATE_EMOTION_VALUES_UNAMBIGUOUS_SMO`, `MODEL_RATE_EMOTION_VALUES_FULL_SMO`, etc.). Confusion matrix classes concatenated with `rbind` (`C1`, `C2`, `C3`, etc.). Classification results reported with names in first array (`C1`, `C2`, `C3`, etc.), and recycled in each subsequent model.

```         
MODEL_RATE_EMOTION_VALUES_UNAMBIGUOUS_SMO = {
rbind(
    C1 = c('C1' = 52.6, 'C2' = 17.1, 'C3' = 0.0, 'C4' = 9.2, 'C5' = 21.1),
    C2 = c(12, 65.2, 7.6, 4.3, 10.9),
    C3 = c(1.1,9.9,73.6,14.3,1.1),
    C4 = c(3.6,10.8,16.9,61.5,7.2),
    C5 = c(21.9,19.2,0,6.8,52.1)
 )
}
MODEL_RATE_EMOTION_VALUES_FULL_SMO = {
rbind(
    C1 = c('C1' = 56.0, 'C2' = 19, 'C3' = 0.0, 'C4' = 7, 'C5' = 18),
    C2 = c(11.3,58.9,13.7,4,12.1),
    C3 = c(0,13.2,68.6,18.2,0),
    C4 = c(4.9,11.7,22.5,54.2,6.7),
    C5 = c(18.5,12.2,1,12.2,56.1)
  )
},
MODEL_RATE_EMOTION_VALUES_FULL_FULLPOLYGONAL = { rbind(
  C1 = c('C1' = 65, 'C2' = 11, 'C3' = 12, 'C4' = 0, 'C5' = 12),
  C2 = c(14.5, 62.1, 22.6, 0.8, 0),
  C3 = c(0, 13.2, 68.6, 18.2, 0),
  C4 = c(0.8, 0, 20.8, 54.2, 24.2),
  C5 = c(38.8, 1, 0, 8.2, 52)
)
},
MODEL_RATE_EMOTION_VALUES_FULL_REDUCEDPOLYGONAL = { 
rbind(
  C1 = c('C1' = 67, 'C2' = 16, 'C3' = 4, 'C4' = 0, 'C5' = 13),
  C2 = c(21.8,55.6,22.6,0,0),
  C3 = c(0,9.1,77.7,13.2,0),
  C4 = c(0,0,23.3,55,21.6),
  C5 = c(27.5,0,0,10.2,62.3)
)
}
```

@@

Validation method used (if applicable). E.g., 10-fold cross validation. Leave one out cross validation. **TODO**: Discuss train/test/validation formatting. When using external validation set, report name? E.g., AcousticBrainz (`alvarez2023ri`)

>>>>

@@

@@

Number of stimuli employed in experiment. If multiple experimental conditions reported, separate $n$ by conditions where possible.

@@

Number of features included in data modeling (if available).

@@

Total number of participants in experiment.

@@

Nature of rating/classification task undertaken by participants. E.g., rate, annotate.

@@

@@

Name(s) of feature analysis toolbox(es).

@@

Name of model type (regression, classification, or both).

@@

Additional information pertaining to predictive model, such as the name of algorithm used and other pertinent parameters. E.g., Random Forest, Commonality Analysis, Multiple Regression, Neural Networks, LDSM.

@@

Metric used in model evaluation. E.g., $R^2$, $MSE$, $CCC$, Classification accuracy, etc.

@@

Additional information pertaining to predictive model. E.g., `training epochs: 100; n layers: 1, 2; LSTM units: 124,248.`

@@

Pertinent prediction of model summaries. Report as *R* named arrays, including summary statistics in variables. When reporting results of multiple models, concatenate multiple entries with `mrbind`. When reporting results for different toolboxes or feature subsets, assign each to a new BiBTeX field with relevant identifier following final underscore. See additional details below.

@@

Validation method used (if applicable). E.g., 10-fold cross validation, leave one out cross validation.

# Encoding study results:

### Regression

Report relevant summary statistics in the `MODEL_RATE_EMOTION_VALUES` field in R code using the following format. Parameters delimited by spaces are later assigned to separate columns in the resulting dataframe.

```         
bind_field(
library.model.features.data.experiment = c(dimension_measure.summaryStat = 0, ...),
...
)
```

## Classification

Confusion matrices can be encoded similarly through a function that assigns relevant meta-parameters to the `model_parameters` attribute of the output matrix. The row names are then replaced with the column names for clearer output. This assumes row names and column names of the confusion matrix are listed in the same order.

```         
confusion_matrix(
library.model.features.data.experiment =  c(class_1 = 0, class_2 = 0, ..., class_n = 0),
class_2 = c(0, 0, ..., 0),
...
)
```

When confusion matrices are not available, encode available parameters (accuracy, precision, recall, $F$ scores, etc.) using the standard nomenclature to distinguish relevant outcomes for each class:

```         
bind_field(
library.model.features.data.experiment = c(class_measure.summaryStat = 0, ...),
...
)
```

### 2024-06-15 studies/library_parser.qmd
update prereg, extraction details

```{r}
bib_file <- read.delim('metaMER_library_extraction_first_pass.bib',
           sep = '@', header = F)

@@

```{r}
## remove bibtext field formatting
# remove curly braces
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\{')) 
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\},'))
# remove first '=' (from bibtex field )
meta_df <- apply(meta_df, 2, function(x) str_remove(x, '='))
# remove double-commas
#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ',,'))
# remove comments
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '%%.*'))
#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
meta_df <- as.data.frame(meta_df)
```

@@

```{r}
eval(parse(text = meta_df$model_rate_emotion_values[4]))
```

@@

```{r}
## function to parse output of multiple models nested within a single cell
parse_model_output = function(df)
{ # loop across rows
  # apply function to replace NAs with empty string
  sapply(1:nrow(df), function(x) {
    df$model_rate_emotion_values <- tidyr::replace_na(df$model_rate_emotion_values, '') # detect cells with rbind in them
    if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
      print('yes')
      # match first model (name between first underscore and rbind)
      model_1_name <- str_match(df$model_rate_emotion_values[x], 
                                "(?<=_).*?(?=rbind)")
      # match subsequent models (name between MODEL_RATE_EMOTION_VALUES_ and rbind)
      model_names <- str_extract_all(df$model_rate_emotion_values[x], 
                                     "(?<=MODEL_RATE_EMOTION_VALUES_).*?(?=rbind)")
      # combine names
      model_names <- unlist(c(model_1_name, model_names))
      # remove special characters
      model_names <- gsub("[^[:alnum:]]", "", model_names)
      # get corresponding values for each model
      model_results <- str_split(df$model_rate_emotion_values[x], 
                "MODEL_RATE_EMOTION_VALUES")
      # get rid of everything up to "rbind"
      model_results <- lapply(model_results, function(x) str_remove(x, 
                                                          '.+?(?=rbind)'))
      # now unlist the models and give them names to add later
      model_results <- unlist(model_results)
       model_results <- paste(model_names, '=', model_results)
      names(model_results) <- model_names
     # return(model_results)
    }
    else { # otherwise, if dealing with non-listed, just return the existing value
      model_results <- df$model_rate_emotion_values[x]
    }
    return(model_results)
  }
    )
  # see whether rbind appears multiple times

@@

```{r}
knitr::kable(get_study_summaries(this_study))
write.csv(get_study_summaries(this_study), "~/testcsv.csv")
```

>>>>

```{r}
bib_file <- read.delim('bib/extractions.bib',
           sep = '@', header = F)

@@

```{r}
## remove bibtext field formatting
# remove curly braces
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\{')) 
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\},'))
# remove first '=' (from bibtex field )
meta_df <- apply(meta_df, 2, function(x) str_remove(x, '='))
# remove double-commas
#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ',,'))
# remove comments
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '%%.*'))
#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
# remove extra characters in final column
meta_df[, ncol(meta_df)] = str_remove_all(meta_df[, ncol(meta_df)], '\\}')
meta_df <- as.data.frame(meta_df)

@@

```{r}
eval(parse(text = meta_df$model_rate_emotion_values[22]))
```

@@

```{r}
## function to parse output of multiple models nested within a single cell
parse_model_output = function(df)
{ # loop across rows
  # apply function to replace NAs with empty string
  sapply(1:nrow(df), function(x) {
    df$model_rate_emotion_values <- tidyr::replace_na(df$model_rate_emotion_values, '') # detect cells with rbind in them
    if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
      # match first model (name between first underscore and rbind)
      model_1_name <- str_match(df$model_rate_emotion_values[x], 
                                "(?<=_).*?(?=rbind)")
      # match subsequent models (name between MODEL_RATE_EMOTION_VALUES_ and rbind)
      model_names <- str_extract_all(df$model_rate_emotion_values[x], 
                                     "(?<=MODEL_RATE_EMOTION_VALUES_).*?(?=rbind)")
      # combine names
      model_names <- unlist(c(model_1_name, model_names))
      # remove special characters
      model_names <- gsub("[^[:alnum:]]", "", model_names)
      # get corresponding values for each model
      model_results <- str_split(df$model_rate_emotion_values[x], 
                "MODEL_RATE_EMOTION_VALUES")
      # get rid of everything up to "rbind"
      model_results <- lapply(model_results, function(x) str_remove(x, 
                                                          '.+?(?=rbind)'))
      # now unlist the models and give them names to add later
      model_results <- unlist(model_results)
       model_results <- paste(model_names, '=', model_results)
      names(model_results) <- model_names
     # return(model_results)
    }
    else { # otherwise, if dealing with non-listed, just return the existing value
      model_results <- df$model_rate_emotion_values[x]
    }
    return(model_results)
  }
    )
  # see whether rbind appears multiple times

@@

```{r}
knitr::kable(get_study_summaries(this_study))
```
